% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}


\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Sentiment Analysis to Predict S\&P 500 Behavior}
\subtitle{[Proposal]}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Aditya Bindra\\
       \affaddr{University of Virginia}\\
       \affaddr{Charlottesville, Virginia}\\
       \email{ab4es@virginia.edu}
% 2nd. author
\alignauthor
Paul Cherian\\
       \affaddr{University of Virginia}\\
       \affaddr{Charlottesville, Virginia}\\
       \email{pmc6dn@virginia.edu}
% 3rd. author
\alignauthor
Ben Haines\\
       \affaddr{University of Virginia}\\
       \affaddr{Charlottesville, Virginia}\\
       \email{bmh5wx@virginia.edu}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\section{Problem Introduction}
The challenge we have decided to address in our project is
how to use publicly available text based information sources
produced by the government in order to predict the behaviors
of financial markets. In particular, our hope is to apply
sentiment analysis techniques to the minutes of the Federal
Open Market Committee (FMOC) in order to identify correlations with
the behaviour of the S\&P 500. The FOMC meets eight times yearly 
and publishes approximately twenty pages of minutes for each meeting.
These minutes discuss the state of the economy and detail a plan
for the monetary policy in the time until the next meeting. The 
frequency of their publication, their scope, and their source 
of a key economic organization leads us to believe that these
documents in particular would be a good source of potential 
insight.

Financial markets are an area where standard
predictive techniques have often been unsuccessful at achieving
accurate results. Stock prices in particular are notorious
for being difficult to forecast. The ability to make accurate 
predictions about economic conditions provides an immediate 
financial incentive for research into this area and an entire 
industry exists whose primary goal is the development of 
techniques to predict market behaviour. Beyond the pursuit of
profit, having a warning period before downturns could 
also potentially allow for protective or even preventative 
actions to be taken. 

Our particular approach to the problem, and the contribution we 
believe separates us from previous similar work, is our combination
of topic modeling and sentiment analysis into a single pipeline. Our
goal is to automatically parse the document to identify different
topics such as the energy or health care markets. Applying
sentiment analysis to these topics individually will allow us to create
predictions for each of the sectors tracked by the S\&P 500.

\section{Related Work}
As mentioned in the previous section, the allure of financial gains
has inspired a large amount of research into the topic of S\&P predictions
in general and sentiment analysis in particular. 

One popular source of data for sentiment analysis is social media. A paper
by Mittal and Goel used sentiment analysis on twitter data in combination
with values from the Dow Jones Industrial Average (DJIA) to predict stock prices.
In comparison to our work this paper used a simpler approach to sentiment
analysis and focused primarily on using a neural network to transform the
output from the analysis into concrete stock predictions. The paper was based
on an earlier 2010 work by Bollen et al that claimed to predict daily DJIA 
fluctuations with 87\% accuracy.\cite{bollen:twitter}

Another common source for data is news articles. For example
Azar in 2009 demonstrated that positive returns could be derived
from text analysis of new sources although a qualification was made
that these returns vanish when trading costs are accounted for.\cite{azar:thesis} In 
contrast to both of these existing works we have chosen an official
government source for data rather than a source that reflects popular opinion.
The benefits of this decision are that our information comes directly from the
entity that decides policy. Downsides are that it limits the amount of data 
available to us and the argument could be made that stock prices are largely
driven by public opinion.

Some previous work has been done on the subject of combining topic modeling and
sentiment analysis by Lu et al.\cite{lu:2011} However, they restrict their application to analyzing
restaurant reviews. We hope that in the process of applying these techniques to our
particular situation we will discover modifications that better suit the algorithms
to this application.

\section{Algorithms and Evaluation}
I don't know how these things work but that should go here. I don't know
how much detail.


%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

%
% End generated code
%

%
%  Use this command to print the description
%
%\printccsdesc

%\keywords{ACM proceedings; \LaTeX; text tagging}

%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{plain}
\bibliography{tmbib}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
%Appendix A
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}
